Learning Auditory Similarities Between Instrumental Playing Techniques

### 2018-01-30 paper/lagrangeSpontaneousSimilarity2017.tex
learnt -> learned (AmE spelling)
whitespace
fix a typo in a comment of mine

\vl{We should probably say a word on the Hornbostel-Sachs taxonomy,
which is based on player-instrument interaction, but is not outdated
given the variety of contemporary music techniques. @biblio}
\ml{great, I was missing such references}

@@

The computational model proposed in this paper is well suited for this kind of search, as it can model complex perceptual timbre spaces and can scale to large databases. Once the features and the projection matrix are computed, the similarity computation is quite effective and can be further enhanced by considering fast similarity search scheme such as locally sensitive least square hashing \cite{pauleve2010locality}. The secondary stage being learnt, it can easily adapt to user tastes and usage history by re-weighting the features for improved search relevance.

>>>>

\vl{We should probably say a word on the Hornbostel-Sachs taxonomy,
which is based on player-instrument interaction, but is now outdated
given the variety of contemporary music techniques. @biblio}
\ml{great, I was missing such references}

@@

The computational model proposed in this paper is well suited for this kind of search, as it can model complex perceptual timbre spaces and can scale to large databases. Once the features and the projection matrix are computed, the similarity computation is quite effective and can be further enhanced by considering fast similarity search scheme such as locally sensitive least square hashing \cite{pauleve2010locality}. The secondary stage being learned, it can easily adapt to user tastes and usage history by re-weighting the features for improved search relevance.
